Mixture-of-tastes Models for Representing Users with Diverse Interests

### 2017-11-12 paper/paper.tex
Change title.
Make changes to use AAAI format.

\documentclass[sigchi]{acmart}

\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{commath}
\usepackage{threeparttable}
\usepackage{caption}
\usepackage{tabularx}

@@

\title{Mixture-of-tastes models for representing users with diverse interests}
\author{Maciej Kula}
\email{maciej.kula@gmail.com}
\date{\today}
\settopmatter{printacmref=false, printccs=false, printfolios=true}
\setcopyright{none}
\acmConference[]{}{}{}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002951.10003260.10003261.10003269</concept_id>
<concept_desc>Information systems~Collaborative filtering</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002951.10003317.10003338.10003346</concept_id>
<concept_desc>Information systems~Top-k retrieval in databases</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Collaborative filtering}
\ccsdesc[500]{Information systems~Top-k retrieval in databases}

\keywords{Recommender Systems, Matrix Factorization, Sequence-based Recommendations}

@@

\subsection{Hyperparameter search}
\begin{figure*}[h]
  \captionsetup{width=.8\linewidth}
  \caption{Maximum test MRR vs number of hyperparameter search iterations. Sequence-based models in the top row; factorization-based models in the bottom row.}
  \label{fig:hyper}
  \includegraphics[width=0.8\textwidth]{includes/hyperparam_search.pdf}
\end{figure*}
Our results are robust to hyperparameter optimization. Figure~\ref{fig:hyper} plots the maximum test MRR achieved by each algorithm as a function of the number of elapsed hyperparameter search iterations. Both baseline and mixture models benefit from hyperparameter tuning. All algorithms converge to their optimum performance relatively quickly, suggesting a degree of robustness to hyperparameter choices. Mixture-LSTM and Embedding Mixture models quickly outperform their baseline counterparts, and maintain a stable performance lead thereafter. This lends support to our belief that the mixture models' superior accuracy reflects their greater capacity to model the recommendation problem well, rather than being an artifact of the experimental procedure or researcher bias.

@@

\bibliography{bibliography}
\bibliographystyle{ACM-Reference-Format}

>>>>

\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{graphicx}
\frenchspacing
% Add additional packages here. The following
% packages may NOT be used (this list
% is not exhaustive:
% authblk, caption, CJK, float, fullpage, geometry,
%hyperref, layout, nameref, natbib, savetrees,
%setspace, titlesec, tocbibind, ulem
%

%
%
% PDFINFO
% You are required to complete the following
% for pass-through to the PDF.
% No LaTeX commands of any kind may be
% entered. The parentheses and spaces
% are an integral part of the
% pdfinfo script and must not be removed.
%
\pdfinfo{
/Title (Mixture-of-tastes Models for Representing Users with Diverse Interests)
/Author (Maciej Kula)
/Keywords (Recommender Systems, Matrix Factorization, Sequence-based Recommendations)
}
%
%Section Numbers
% Uncomment if you want to use section numbers
% and change the 0 to a 1 or 2
% \setcounter{secnumdepth}{0}
% Title and Author Information Must Immediately Follow
% the pdfinfo within the preamble
%

\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{commath}
\usepackage{threeparttable}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{natbib}

@@

%US Lettersize Paper Is Required

\title{Mixture-of-tastes Models for Representing Users with Diverse Interests}
\author{Maciej Kula\\maciej.kula@gmail.com}
%\email{maciej.kula@gmail.com}
\date{\today}
%\settopmatter{printacmref=false, printccs=false, printfolios=true}
%\setcopyright{none}
%\acmConference[]{}{}{}

%% \begin{CCSXML}
%% <ccs2012>
%% <concept>
%% <concept_id>10002951.10003260.10003261.10003269</concept_id>
%% <concept_desc>Information systems~Collaborative filtering</concept_desc>
%% <concept_significance>500</concept_significance>
%% </concept>
%% <concept>
%% <concept_id>10002951.10003317.10003338.10003346</concept_id>
%% <concept_desc>Information systems~Top-k retrieval in databases</concept_desc>
%% <concept_significance>500</concept_significance>
%% </concept>
%% </ccs2012>
%% \end{CCSXML}

%\ccsdesc[500]{Information systems~Collaborative filtering}
% \ccsdesc[500]{Information systems~Top-k retrieval in databases}

% \keywords{Recommender Systems, Matrix Factorization, Sequence-based Recommendations}

@@

\subsection{Hyperparameter search}
  \begin{figure*}[h]
    \centering
    \captionsetup{width=.8\linewidth}
    \caption{Maximum test MRR vs number of hyperparameter search iterations. Sequence-based models in the top row; factorization-based models in the bottom row.}
    \label{fig:hyper}
    \includegraphics[width=0.8\textwidth]{includes/hyperparam_search.pdf}
  \end{figure*}

Our results are robust to hyperparameter optimization. Figure~\ref{fig:hyper} plots the maximum test MRR achieved by each algorithm as a function of the number of elapsed hyperparameter search iterations. Both baseline and mixture models benefit from hyperparameter tuning. All algorithms converge to their optimum performance relatively quickly, suggesting a degree of robustness to hyperparameter choices. Mixture-LSTM and Embedding Mixture models quickly outperform their baseline counterparts, and maintain a stable performance lead thereafter. This lends support to our belief that the mixture models' superior accuracy reflects their greater capacity to model the recommendation problem well, rather than being an artifact of the experimental procedure or researcher bias.

@@

\bibliography{bibliography}
\bibliographystyle{aaai}
